\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{hyperref}

% Page margins
\geometry{
  left=2.5cm,
  right=2.5cm,
  top=2cm,
  bottom=2cm
}

% Sender information
\address{Erfan Taghvaei \\
Kaiserslautern, Germany \\
+49 157 35338285 \\
etaghvaei0098@gmail.com}

% Date
\date{\today}

\begin{document}

% Recipient
\begin{letter}{%
growney GmbH \\
Berlin, Germany
}

\opening{Dear growney Team,}

I am writing to express my strong interest in the Working Student Software Development position at growney. The opportunity to contribute to a real digital transformation project -- migrating from a PHP monolith to a modern serverless architecture -- is exactly the kind of challenging learning experience I'm seeking. Moreover, I am very motivated to relocate to Berlin, as I find it a much more vibrant and dynamic city than Kaiserslautern, offering better opportunities for both my professional growth and personal development.

I am currently pursuing a Master's degree in Computer Science at RPTU Kaiserslautern with a focus on Software Engineering. I bring two years of professional software development experience at Neocosmo in Germany, where I worked as a React Native Developer on various client projects for companies including Festo, KVNO, Riniger, and Hochschule Kempten. During this time, I gained hands-on experience with the full software development lifecycle in agile teams, from requirements analysis to production deployment. I have extensive practical experience with JavaScript and TypeScript through two years of React Native development, solid knowledge of React for web applications demonstrated through my RecallCards project where I built a complete fullstack application with React frontend, backend development experience with Flask and REST APIs which gives me a strong foundation for working with Node.js, hands-on experience with MySQL and relational databases as well as NoSQL databases like MongoDB and Redis, practical DevOps experience including Docker containerization for consistent deployments across environments, GitLab CI/CD pipelines for automated testing and deployment, and working with cloud technologies and deployment processes. I have independently developed several fullstack projects including RecallCards, a flashcard application with React frontend, Flask backend, Auth0 authentication, Redis session management, fully containerized with Docker and deployed with NGINX and GitHub Actions CI/CD, and an AAS Sanity project featuring a web application with multi-threading optimization and automated data processing.

I am particularly excited about growney's tech transformation because I understand the challenges and opportunities of modernizing legacy systems. My experience with Docker containerization, microservice thinking through my fullstack projects, and CI/CD automation aligns well with your migration to a cloud-native architecture. I am motivated to learn, detail-oriented, and eager to contribute to real production systems. My MongoDB Associate Developer certification from 2024 demonstrates my commitment to continuous learning and staying current with modern technologies. I am a team player who enjoys solving complex technical challenges and has experience collaborating with developers and stakeholders in agile environments. I speak and write English fluently and have very good German skills. Most importantly, I am ready and excited to relocate to Berlin and become part of the vibrant tech scene there. Working in Berlin would be a significant step forward for my career, and I am fully committed to making this move to join growney's ambitious team.

I am convinced that my practical software development experience, my motivation to learn modern cloud technologies, and my genuine enthusiasm for Berlin and growney's mission make me a valuable addition to your team. I would be thrilled to discuss how I can contribute to your platform transformation.

\closing{Sincerely,}

\end{letter}

\end{document}
