\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman,english]{babel}
\usepackage{geometry}
\usepackage{hyperref}

% Page margins
\geometry{
  left=2.5cm,
  right=2.5cm,
  top=2cm,
  bottom=2cm
}

% Sender information
\address{Erfan Taghvaei \\
Kaiserslautern, Deutschland \\
+49 157 35338285 \\
etaghvaei0098@gmail.com}

% Date
\date{\today}

\begin{document}

% Recipient
\begin{letter}{%
Siemens Energy Global GmbH \& Co. KG \\
Transformation of Industry \\
Karlsruhe, Baden-Württemberg \\
Deutschland
}

\opening{Dear Siemens Energy Team,}

I am writing to express my strong interest in the Working Student (f/m/d) Junior Software Developer position within your Transformation of Industry division. The opportunity to develop cutting-edge AI applications that integrate artificial intelligence with process automation technologies, while contributing to the decarbonization of the industrial sector, deeply resonates with my career aspirations.

\textbf{Why Siemens Energy:}

Your mission to decarbonize the industrial sector and drive the energy transition represents exactly the kind of impactful work I want to contribute to. The combination of AI technologies, process automation systems, and sustainable energy solutions offers a unique learning opportunity that aligns perfectly with my technical background and personal values.

\textbf{My Technical Qualifications:}

I bring two years of professional software development experience in Germany at Neocosmo, where I worked as a React Native Developer on various customer projects for companies including Festo, KVNO, Riniger, and Hochschule Kempten. I am particularly proud of a project where I independently handled a critical ticket over two months, working directly with the customer to successfully resolve all issues.

\textbf{Relevant Technical Skills:}

\begin{itemize}
  \item \textbf{Python Programming}: Extensive experience with Python and Flask framework -- developed multiple projects including a web application with multi-threading optimization and a full-stack flashcard application with backend logic
  \item \textbf{Software Development Principles}: Strong foundation in clean code, software architecture, and design patterns from both academic coursework and professional experience
  \item \textbf{Git \& Version Control}: Daily work with Git, experience with GitLab CI/CD pipelines and collaborative development
  \item \textbf{Agile Methodologies}: Two years of experience working in agile teams with regular code reviews, sprint planning, and iterative development
  \item \textbf{Problem-Solving}: Proven analytical skills through algorithm optimization projects and troubleshooting complex software issues
  \item \textbf{Documentation}: Experience creating automated documentation with GitLab YAML scripts and maintaining comprehensive project documentation
  \item \textbf{Testing}: Hands-on experience with automated testing frameworks (Detox, Storybook) and quality assurance practices
  \item \textbf{Linux}: Daily work with Linux systems and command-line tools for development and deployment
\end{itemize}

\textbf{Process Automation Interest:}

While I am eager to deepen my knowledge of PLC, DCS, and SCADA systems, my background in software-hardware integration provides a solid foundation. Through my work with React Native applications that interface with various hardware components and sensors, I have developed an understanding of how software interacts with physical systems. I am excited to expand this knowledge into industrial process automation.

\textbf{Academic Background:}

I am currently pursuing a Master's degree in Computer Science at RPTU Kaiserslautern, with focus areas in Software Engineering, Data Visualization, and Network Security. My coursework includes relevant subjects such as Compiler Design, Data Structures and Algorithms, and Operating Systems -- providing the theoretical foundation necessary for developing complex software systems. My Bachelor's degree in Software Engineering from Tehran Azad University further strengthens my technical foundation.

\textbf{What I Bring to Your Team:}

\begin{itemize}
  \item \textbf{Collaborative Mindset}: Two years of experience working closely with cross-functional teams, customers, and stakeholders
  \item \textbf{Proactive Learning}: Quick adaptation to new technologies -- recently earned MongoDB Associate Developer certification (2024)
  \item \textbf{Quality Focus}: Strong emphasis on writing clean, efficient, and well-documented code
  \item \textbf{Communication Skills}: Excellent German (C1) and English (C2) proficiency, enabling effective collaboration in international teams
  \item \textbf{Passion for Technology}: I program in my free time and am genuinely excited about solving technical challenges
\end{itemize}

The values that Siemens Energy upholds -- diversity, inclusion, and innovation -- strongly resonate with me. Your commitment to creating an environment where different perspectives generate creative energy is exactly the kind of workplace where I thrive. As someone who has worked and studied in multiple countries, I deeply appreciate the value that diverse teams bring to innovation.

The opportunity to work on AI-driven solutions for process automation while contributing to the global energy transition would be an ideal next step in my career. I am eager to learn from your experienced team of Process Automation Engineers and contribute my software development skills to impactful projects.

I am excited about the possibility of joining Siemens Energy and contributing to your mission of making sustainable, reliable, and affordable energy a reality. I would welcome the opportunity to discuss how my skills and enthusiasm can benefit your team.

Thank you for considering my application. I look forward to speaking with you.

\closing{Sincerely,}

\end{letter}

\end{document}
